---
title: 'IT497 Fall 2016 Exam #1 Part 2'
author: "Nishant Kuhar"
date: "10/1/2016"
output: html_document
---
1.
Creating Data Frame and naming it df.
```{r}
df<-read.csv("http://www.itk.ilstu.edu/faculty/jrwolf/wit.csv")
```
a.
Creating a variable x, and comparing value to find row with Reddit company Data
num_of_female_eng variable shows number of female software eng. working in Reddit
```{r}
x<-c("reddit")
num_of_female_eng<-c(df[is.element(df$key,x),])
num_of_female_eng$num_female_eng
```
b.Sum shows the total number of females working.
```{r}
sum(df$num_female_eng)
```

2.
Creating Data Frame and naming it usBirthData.
```{r}
### Start usBirthData Code#######
install.packages("rvest")
library("rvest")

usBirthData <- read_html("https://www.ssa.gov/oact/babynames/numberUSbirths.html")
usBirthData <- html_table(html_node(usBirthData, "table.border"), header=TRUE)
names(usBirthData) <- c("Year", "Female", "Male", "Total")
### End usBirthData Code #######
```
a.The year with most children.
"maxNoOfBirths" variable defines the highest number of births in any year.
Then we compare the maxNoOfBirths with the row that contains it and find the year.
```{r}
maxNoOfBirths<-max(usBirthData$Total)
usBirthData$Year[is.element(usBirthData$Total,maxNoOfBirths)]
```

b.
"minNoOfBirths" variable defines the lowest number of births in any year.
Then we compare the minNoOfBirths with the row that contains it and find the year.
```{r}
minNoOfBirths<-min(usBirthData$Total)
usBirthData$Year[is.element(usBirthData$Total,minNoOfBirths)]
```

3.

Loading the table from url and making data frame topCities
```{r}
topCities <- read_html("https://en.wikipedia.org/wiki/List_of_cities_proper_by_population")
topCities <- html_table(
        html_node(
                topCities, "table.sortable"
        ), header=TRUE, trim=TRUE
)
names(topCities) <- c(
        "Rank", "City", "Image", "Population", "Definition",
        "Total.Area", "Population.Density", "Country"
)
topCities$Image <- NULL
topCities$Population <- as.numeric(
        gsub(",", "",
                gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1", topCities$Population)
        )
)
topCities$Definition <- gsub("^([^\\[]+).*$", "\\1", topCities$Definition)
topCities$Total.Area <- as.numeric(
        gsub(",", "",
                gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1", topCities$Total.Area)
        )
)
topCities$Population.Density <- as.numeric(gsub(",", "", topCities$Population.Density))
```

Problem with the data set cannot compare the country column to its corresponding values
```{r}
topCities$Country==" India"
topCities$Country=="India"
x<- topCities[is.element(topCities$Country,"India"),]
x<- x[ order(x$Total.Area,decreasing = T) ]
x$City[1:5]
```
way to do it
code:
x<- topCities[is.element(topCities$Country,"India"),]
x<- x[ order(x$Total.Area,decreasing = T) ]
x$City[1:5]

Similarly for b part


4.Creating Data Frame and naming it snp500.
```{r}
########## SnP Code Start ##############
snp500 <- read_html("https://en.wikipedia.org/wiki/List_of_S%26P_500_companies")
snp500 <- html_table(
        html_node(
                snp500, "table.wikitable:nth-child(6)"
        ), header=TRUE
)
names(snp500) <- c(
        "Ticker", "Name", "SEC.Filing", "GICS.Sector",
        "GICS.SubIndustry", "Location.HQ", "Date.Added", "CIK"
)
########## SnP Code End ##############
```
a.Names of firms added in S&P500 since 2010
  Declare a variable x with the value of "2010-01-01". Compare and show results.
```{r}
x<-c("2010-01-01")
snp500$Name[snp500$Date.Added>=x]
```

b.Number of firms in the table. 
The answer is simply calculating the number of rows which corresponds to the number of firms.
```{r}
nrow(snp500)
```


5.
Defining a Data Frame called: venues
```{r}
 ### Start Venue R Code ####
 cricket_world_cup <- read_html("http://en.wikipedia.org/wiki/2015_Cricket_World_Cup")
 venues = html_table(html_nodes(cricket_world_cup, "table")[[5]])
 ### End Venue R Code ####
```
Viewing the str of venues
```{r}
 str(venues)
```
 As we can see the capacity col in venues is of char data type changing it to numeric data type
 using gsub
```{r}
 venues$Capacity<- venues$Capacity
venues$Capacity<-as.numeric(gsub(",", "", venues$Capacity))
```
 a. Maximun capacity venue name
```{r}
MaxCapacity <- max(venues$Capacity)
venueNameWithMaxCapacity<- venues$Venue[is.element(venues$Capacity,MaxCapacity)]
venueNameWithMaxCapacity
```

b. Minimum capacity venue name

```{r}
MinCapacity <- min(venues$Capacity)
venueNameWithMinCapacity<- venues$Venue[is.element(venues$Capacity,MinCapacity)]
venueNameWithMinCapacity
```